---
title: "calss lab4"
author: "YI-Hung, Lu"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

1) For the lists given above, show and use R code (a map function) to iteratively
find the square of the sums across the vectors
```{r}
x <- list(2, 4, 5, 9, 1)
y <- list(8, 7, 2, 8, 3)
z <- list(1, 8, 5, 4, 2)
```

```{r}
pmap_dbl(list(x,y,z), function(first, second, third) (first + second + third)^2)
```


2) Using the data table above, use and show R code that will output a statement that
is descriptive for all rows of the data table.
The first row is given below. Your code should produce the other specific statements. John who is Male, has a salary that is 65000 dollars per year.
```{r}
tribble( ~Student, ~Gender, ~Salary,
"John", "Male", 65000,
"Alice", "Female", 73000,
"Juan", "Male", 66000,
"Beth", "Female", 71500,
"Denise", "Female", 82000
) -> table
table
```

```{r}
table%>% 
  pmap_chr(~ str_glue("{..1} who is {..2}, has a salary that is {..3} dollars per year."))
```


3) Write a nested loop that will produce a 5 by 5 matrix that whose matrix elements
are sums of the corresponding columns and rows.
Your code should produce the matrix below:
```{r}
matrix_sum <- matrix(0, nrow = 5, ncol = 5)
for (i in 1:5) {
  for (j in 1:5) {
    matrix_sum[i, j] <- i + j
  }
}
print(matrix_sum)

```

4) Use for loop coding to produce the number sequence shown below:
Note that the numbers 5 and 10 are missing
```{r}
x <- 1:20
for (val in x) {
  if (val == 5 | val == 10){
    next
  }
  print(val)
}
```

